Presentation Title

### 2017-08-23 thesis/chapters/ch3-model.tex
Rearrange figures; edit

In this chapter, we break away from the early blockchain paradigm and introduce a novel system that is application neutral,
horizontally scalable and will never have a block size debate.
In particular, our system consists of three protocols---the consensus protocol, the transaction protocol and the validation protocol.
It is based on our prior research on TrustChain~\cite{multichain} at Delft,
where every node independently interacts with each other via their own hash chain\footnote{TrustChain is originally called MultiChain but the name has changed to TrustChain}.

@@

\subsection*{TrustChain and Extended TrustChain}
We first describe the standard TrustChain and then the Extended TrustChain.
Our description of the standard TrustChain has a minor difference when compared to the description in~\cite{multichain},
we remark the difference when it occurs.

% \subsubsection*{Standard TrustChain}
In TrustChain, every node has a ``personal'' hash chain. 
Initially, the chain only contains a genesis block generated by the nodes themselves.
When node $A$ wishes to add a new transaction (TX) with $B$,
a new TX block is generated for both $A$ and $B$ and is appended to their respective chains.
The TX block must have a valid hash pointer pointing to the previous block and a reference\footnote{This definition is different from the original TrustChain definition found in~\cite{multichain}.
    In the original definition, a TX block has two outgoing edges which are hash pointers to the two parties involved in the transaction.
    This work uses one outgoing edge and a reference.} to its \emph{pair} on $B$'s chain.
An example of is shown in \Cref{fig:trustchain-bad}.

\begin{figure}
    \includegraphics[width=0.9\textwidth]{trustchain-bad}
    \centering
    \caption{
    A TrustChain example with three nodes.
    Every block is denoted by $t_{i,j}$, where $i$ is the node ID and $j$ is the sequence number of the block.
    The arrows represent hash pointers and the dotted lines represent references.
    The blocks at the ends of the dotted lines are pairs of each other.
    The red block behind $t_{b, 6}$ indicates a fork.
    Blocks of index 0 (e.g. $t_{b, 0}$) are genesis blocks.}
    \label{fig:trustchain-bad}
\end{figure}

@@

% \subsubsection*{Extended TrustChain}
Extended TrustChain introduces a new block type---checkpoint (CP) block.
The primary function of the CP block is to represent the state of a node, in the form of a hash pointer.
A collection of CP blocks from all nodes represents the state of the whole system.
Therefore, nodes need to reach consensus on CP blocks using some consensus protocol, which we explain next.
A visual representation is shown in \Cref{fig:trustchain-bad-cp}.

@@

\begin{figure}
    \includegraphics[width=0.9\textwidth]{trustchain-bad-cp}
    \centering
    \caption{An example of Extended TrustChain.
    The circles represent CP blocks,
    they also have hash pointers (arrow) but do not have references (dotted line).
    Note that the sequence number counter does not change, it is shared with TX blocks.
    CP blocks of index 0 (e.g. $c_{b, 0}$) are genesis blocks.}
    \label{fig:trustchain-bad-cp}
\end{figure}

@@

The consensus protocol can be seen as a technique of running infinitely many times of a Byzantine consensus algorithm\footnote{More accurately it is an asynchronous common subset (ACS) algorithm, which we describe in \Cref{sec:acs-background}.},
starting a new execution immediately after the previous one is completed.
This approach is necessary because blockchain systems always need to reach consensus on new values proposed by the nodes in the system,
or CP blocks in our case.

The communication complexity of Byzantine consensus algorithms typically grows polynomially w.r.t the number of nodes,
which prohibits us from running it on a large network.
For example, one of the most recent works tested with up to 104 nodes and the algorithm took almost 6 minutes to complete~\cite{miller2016honey}.
Thus, at the beginning of every Byzantine consensus algorithm execution,
we randomly elect a set of nodes---called facilitators---to collect CP blocks from every other node and use those blocks as the input to the Byzantine consensus algorithm, and then run it.
After the algorithm completes,
the facilitators output a set of CP blocks which we call the consensus result.
The result is then propagated to the network,
and the next algorithm execution begins.

@@

The consensus and transaction protocol by themselves do not provide a mechanism to detect malicious behaviour such as tampering the TrustChain.
Thus, we need a validation protocol to counteract such behaviour.
When a node wishes to validate one of its transactions, it asks the counterparty for the \emph{agreed fragment} of the transaction.
Which is a fragment of the counterparty's chain beginning and ending with CP blocks but contains the TX block belonging to that transaction,
the CP blocks must also be in consensus.
Upon the counterparty's response,
the node checks whether the CP blocks are in some consensus result and some other conditions.
The TX is valid if these conditions are satisfied.
Intuitively, this works because it is hard (because a cryptographically secure hash function is collision resistant)
to create a different chain that begins and ends with the same two CP blocks.

@@

We assume purely asynchronous channels with eventual delivery.
Thus in no stage of our protocol do we make timing assumptions.
The adversary has full control of the delivery schedule and the message ordering of all messages.
% But they are not allowed to drop messages except for their own\footnote{
%     Reliability can be achieved in unreliable networks by resending messages or using some error correction code.
% }.

@@

% TODO big N does not follow our convention
In our model, we consider $N$ nodes, which is the population size.
$n$ of them are facilitators, $t$ nodes are malicious and the inequality
$n \ge 3t + 1$ must hold.
This inequality is from the work of Pease, Shostak and Lamport, where they show a network of $n$ nodes cannot reach Byzantine agreement with $t \ge n/3$~\cite{pease1980reaching}.
Further, the inequality $N \ge n + t$ must also hold so that there are enough honest nodes in the network to run the consensus protocol;
the exact reason becomes apparent in~\Cref{sec:consensus-phase}.

@@

\section{Extended TrustChain}
The primary data structure used in our system is the Extended TrustChain.
Each node $u$ has a public and private key pair---$pk_u$ and $sk_u$, and a chain $B_u$.
The chain consist of blocks $B_u = \{ b_{u, i} : i \in \{ 0, \dots, h - 1 \} \}$,
where $b_{u, i}$ is the $i$th block of $u$,
and $h$ is the height of the block (i.e. $h = |B_u|$).
We use $b_{u, h}$ to denote the latest block.
There are two types of blocks, TX blocks and CP blocks.
If $T_u$ is the set of all TX blocks in $B_u$ and $C_u$ is the set of all CP blocks is $B_u$,
then $T_u \cup C_u = B_u$ and $T_u \cap C_u = \varnothing$.
The notation $b_{u, i}$ is generic over the block type.
% We assume there exists a function $\textsf{typeof}: B_u \rightarrow \{ \tau, \gamma \}$ that returns the type of the block,
% where $\tau$ represents the TX type and $\gamma$ represents the CP type.

@@

The TX block is a six-tuple, i.e
$$t_{u, i} = \langle \textsf{H}(b_{u, i - 1}), seq_u, txid, pk_v, m, sig_u \rangle.$$
We describe each item in turn.
\begin{enumerate}
\item $\textsf{H}(b_{u, i - 1})$ is the hash pointer to the previous block.
\item $seq_u$ is the sequence number, which should equal $i$.
\item $txid$ is the transaction identifier, it should be generated using a cryptographically secure pseudo-random number generator by the initiator of the transaction.
\item $pk_v$ is the public key of the counterparty $v$.
\item $m$ is the transaction message.
\item $sig_u$ is the signature created using $sk_u$ on the concatenation of the binary representation of the five items above.
\end{enumerate}
The fact that we have no constraint on the content of $m$ is in alignment with our design goal---application neutrality.

TX blocks come in pairs.
In particular, for every TX block 
$$t_{u, i} = \langle \textsf{H}(b_{u, i - 1}), seq_u, txid, pk_v, m, sig_u \rangle$$
there exist one and only one \emph{pair} 
$$t_{v, j} = \langle \textsf{H}(b_{v, j - 1}), seq_v, txid, pk_u, m, sig_v \rangle,$$
if they are created by honest nodes running the TX protocol.
Note that the $txid$ and $m$ are the same, and the public keys refer to each other.
Thus, given a TX block, these properties allow us to identify its pair.
\end{definition}

@@

Our consensus protocol runs in rounds,
where the first round is defined to be 1 and it is incremented after every execution of the consensus protocol.
The consensus result is a tuple, i.e. 
$$\C_r = \langle r, C \rangle,$$
where $C$ is a set of CP blocks agreed by the facilitators of round $r$.
\end{definition}

Here we define an important property which results from the interleaving nature of CP and TX blocks.
It is used in our validation protocol.
\begin{definition}
\textbf{\emph{Enclosure and agreed enclosure}}

@@

If the enclosure of some TX block $t_{u, i}$ is $\langle c_{u,a}, c_{u, b} \rangle$,
then its \emph{fragment} $F_{u, i}$ is defined as $\{ b_{u, i} : a \le i \le b \}$.
Similarly, \emph{agreed fragment} has the same definition as fragment but using agreed enclosure.
For convenience, the function $\textsf{agreed\_fragment}(t_{u, i})$ outputs the agreed fragment of $t_{u, i}$ if it exists, otherwise $\bot$.
\end{definition}

@@

Our consensus protocol $\Pi_c$ runs on top of the Extended TrustChain.
It uses an unmodified asynchronous common subset (ACS) algorithm as the key building block.
The objectives of the protocol are to
    allow honest nodes always make progress (in the form of creating new CP blocks),
    compute correct consensus result in every round
    and have an unbiased election of facilitators.
We formally define the desired properties below.
\begin{definition}
\label{def:consensus}
\textbf{\emph{TrustChain consensus protocol}}

@@

There are $n$ nodes, of which at most $t$ might experience Byzantine fault.
Node $i$ starts with a non-empty set of input values $C_i$.
The nodes must decide an output $C$, satisfying the following.
\begin{enumerate}
    \item \emph{Agreement:}
        If a correct node outputs $C$, then every node outputs $C$.
    \item \emph{Validity:}
        If any correct node outputs a set $C$,
        then $|C| \ge n - t$ and $C$ contains the input of at least $n - 2t$ nodes.
    \item \emph{Termination:}
        If $n - t$ nodes receive an input, then all correct nodes produce an output.
\end{enumerate}
\end{definition}

ACS has the nice property of censorship resilience when compared to other consensus algorithms.
In PBFT~\cite{castro1999practical}, a leader is elected, if the leader is malicious but follows the protocol, then it can selectively filter transactions.
In contrast, every party in ACS are involved in the proposal phase,
and it guarantees that if $n - 2t$ parties propose the same transaction, then it must be in the agreed output.
Thus, if some value is submitted to at least $n - 2t$ nodes, it is guaranteed to be in the consensus result.
For a detailed description of ACS, we refer to the HoneyBadgerBFT work~\cite{miller2016honey}.
To understand the remainder of this work, the knowledge of~\Cref{def:acs} is sufficient.

@@

To bootstrap, imagine that there is some bootstrap oracle that initiates the correct program on every node,
meaning that it satisfied the properties in \Cref{def:consensus}.
This concludes the bootstrap phase.
For any future rounds, the consensus phase is used.

In practice, the bootstrap oracle is most likely the software developer that sets up the system and assigns the facilitators of round 1 in a fair way.

\subsection{Consensus phase}
\label{sec:consensus-phase}
For any node $u$,
the consensus phase begins when $\F_r$ is available and the latest block is $c_{u, h}$.
Note that $\F_r$ indicates the facilitators that were elected using results of round $r$ and are responsible for driving the ACS algorithm in round $r + 1$.
The goal is to reach agreement on a set of new facilitators $\F_{r + 1}$ that satisfies the four properties in \Cref{def:consensus}.

There are two scenarios in the consensus phase.
First, if $u$ is not the facilitator, it sends $\langle \texttt{cp\_msg}, c_{u, h} \rangle$ to all the facilitators.
Second, if $u$ is a facilitator, it waits until $N - t$ messages of type \texttt{cp\_msg} are received.
% Second if the node is a facilitator, it waits for some duration $D$ and collect messages of type \texttt{cp\_msg}, where $D \gg \Delta$.
Invalid messages are removed.
That is blocks with invalid signatures and blocks signed by the same key.
With the sufficient number of \texttt{cp\_msg} messages,
it begins the ACS algorithm and some $\C'_{r + 1}$ should be agreed upon by the end of it.
Duplicates and blocks with invalid signatures are again removed from $\C'_{r+1}$ and we call the final result $\C_{r+1}$.
We have to remove invalid blocks a second time because the adversary may send different CP blocks to different facilitators,
which results in invalid blocks in the ACS output, but not in any of the inputs.

@@

Continuing, when $\F_{r}$ finish the ACS execution and reach agreement on $\C_{r+1}$,
they immediately broadcast two messages to all the nodes---
first the consensus message $\langle \texttt{cons\_msg}, \C_{r+1} \rangle$,
and second the signature message $\langle \texttt{cons\_sig}, r, sig \rangle$.
The reason for sending \texttt{cons\_sig} is the following.
The channels are not authenticated, 
and there are no signatures in $\C_{r + 1}$.
If a non-facilitator sees some $\C_{r + 1}$, it cannot immediately trust it because it may have been forged.
Thus, to guarantee authenticity, every facilitator sends an additional message that is the signature of $\C_{r + 1}$.

@@

The TX protocol $\Pi_t$, shown in \Cref{alg:tx-proto}, is run by all nodes.
It is also known as True Halves, first described informally by Veldhuisen~\cite[Chapter~3.2]{truehalves}.
Nodes that wish to initiate a transaction calls $\textsf{new\_tx}(pk_v, m, txid)$ (\Cref{alg:new-tx}) with the intended counterparty $v$ identified by $pk_v$ and message $m$.
$txid$ should be a uniformly distributed random value, i.e. $txid \in_R \{0, 1\}^{256}$.
Then the initiator then sends $\langle \texttt{tx\_req}, t_{u, h}\rangle$ to $v$.

@@

The consensus protocol and the validation protocol do not provide a mechanism to detect tampering.
The validation protocol aims to solve this issue.
The protocol is also a request-response protocol, just like the transaction protocol.
It assumes that nodes store all the consensus results that are aware of.
But before explaining the protocol itself, we first define what it means for a transaction to be valid.

@@

\begin{algorithm}
\caption{Function $\textsf{get\_validity}(t_{u, i}, F_{u, i}, F_{v, j})$ validates the transaction represented by $t_{u, i}$.
We assume $F_{u, i}$ is always correct and contains $t_{u, i}$.
$F_{v, j}$ is the corresponding fragment received from $v$.}
\label{alg:get-validity}

@@

A TrustChain validation protocol is correct if the following properties hold.
\begin{enumerate}
    \item \emph{Agreement}:
        If any correct node decides on the validity (except when it is \emph{unknown}) of a transaction,
        then all other correct nodes are able to reach the same conclusion or output \emph{unknown}.
    \item \emph{Validity}:
        The validation protocol outputs the correct result
        according to the aforementioned validity definition.
    % \item \emph{Unforgeability}:
    %     If some transaction is valid, it cannot be forged into an invalid transaction.
    %     If some transaction is invalid, it cannot be forged into a valid transaction.
    \item \emph{Liveness}:
        Any valid (invalid) transaction is marked as valid (invalid) eventually.
\end{enumerate}
\end{definition}

>>>>

In this chapter, we break away from the early blockchain paradigm and introduce a novel system that is application neutral,
horizontally scalable and will never have a block size debate.
In particular, our system consists of three protocols---the consensus protocol, the transaction protocol and the validation protocol.
It is based on our prior research on TrustChain~\cite{multichain} at Delft,
where every node independently interacts with each other via their own hash chain\footnote{TrustChain is originally called MultiChain.}.

@@

\subsection*{TrustChain and Extended TrustChain}
We explain the standard TrustChain first and then the Extended TrustChain.
Our description of the standard TrustChain has a minor difference when compared to the description in~\cite{multichain},
we remark the difference when it occurs.

% \subsubsection*{Standard TrustChain}
In TrustChain, every node has a personal hash chain. 
Initially, the chain only contains a genesis block generated by the nodes themselves.
When node $A$ wishes to make a transaction (TX) with $B$,
a new TX block is generated for both $A$ and $B$ and is appended to their respective chains.
The TX block must have a valid hash pointer pointing to the previous block and a reference\footnote{This definition is different from the original TrustChain definition found in~\cite{multichain}.
    In the original definition, a TX block has two outgoing edges which are hash pointers to the two parties involved in the transaction.
    This work uses one outgoing edge and a reference.} to its \emph{pair} on $B$'s chain.
An example of is shown in \Cref{fig:trustchain-bad}.

\begin{figure}
    \includegraphics[width=1\textwidth]{trustchain-bad}
    \centering
    \caption{
    A TrustChain example with three nodes.
    Every block is denoted by $t_{i,j}$, where $i$ is the node ID and $j$ is the sequence number of the block.
    The arrows represent hash pointers and the dotted lines represent references.
    The blocks at the ends of the dotted lines are pairs of each other.
    The red block behind $t_{b, 6}$ indicates a fork.
    Blocks of index 0 (e.g. $t_{b, 0}$) are genesis blocks.}
    \label{fig:trustchain-bad}
\end{figure}

@@

% \subsubsection*{Extended TrustChain}
Extended TrustChain introduces a new block type---checkpoint (CP) block.
The primary function of the CP block is to represent the state of a node, in the form of a hash pointer.
A collection of CP blocks from all nodes represents the state of the whole system.
Therefore, nodes need to reach consensus on CP blocks using some consensus protocol in order to reason about the state,
which we explain next.
A visual representation is shown in \Cref{fig:trustchain-bad-cp}.

@@

\begin{figure}
    \includegraphics[width=1\textwidth]{trustchain-bad-cp}
    \centering
    \caption{An example of Extended TrustChain.
    The circles represent CP blocks,
    they also have hash pointers (arrow) but do not have references (dotted line).
    Note that the sequence number counter does not change, it is shared with TX blocks.
    CP blocks of index 0 (e.g. $c_{b, 0}$) are genesis blocks.}
    \label{fig:trustchain-bad-cp}
\end{figure}

@@

The consensus protocol can be seen as a technique of running infinitely many times of a Byzantine consensus algorithm\footnote{More accurately it is an asynchronous common subset (ACS) algorithm, which we describe in \Cref{sec:acs-background}.},
starting a new execution immediately after the previous one is completed.
Nodes create new CP blocks at the end of every execution.
This approach is necessary because blockchain systems always need to reach consensus on new values proposed by the nodes in the system,
or CP blocks in our case.

The communication complexity of Byzantine consensus algorithms typically grows polynomially w.r.t the number of nodes,
which prohibits us from running it on a large network.
For example, one of the most recent works tested with up to 104 nodes and the algorithm took almost 6 minutes to complete~\cite{miller2016honey}.
Thus, at the beginning of every Byzantine consensus algorithm execution,
we randomly elect a set of nodes---called facilitators---to collect CP blocks from every other node and use those blocks as the input to the Byzantine consensus algorithm, and then run it.
After the algorithm completes,
the facilitators output a set of CP blocks which we call the consensus result,
which is then propagated to the network.
Using the result, nodes are allowed to create new CP blocks,
and then the next algorithm execution begins.

@@

The consensus and transaction protocol by themselves do not provide a mechanism to detect malicious behaviour such as tampering the TrustChain.
Thus, we need a validation protocol to counteract such behaviour.
When a node wishes to validate one of its transactions, it asks the counterparty for the \emph{agreed fragment} of the transaction.
Which is a fragment of the counterparty's chain beginning and ending with CP blocks but contains the TX block belonging to that transaction,
and the CP blocks must be in consensus.
Upon the counterparty's response,
the node checks whether the CP blocks are in some consensus result and some other conditions.
The transaction is valid if these conditions are satisfied.
Intuitively, this works because it is hard (because a cryptographically secure hash function is collision resistant)
to create a different chain that begins and ends with the same two CP blocks.

@@

We assume purely asynchronous channels with eventual delivery.
Thus in no stage of our protocol do we make timing assumptions.
The adversary has full control of the delivery schedule and the ordering of all messages.
% But they are not allowed to drop messages except for their own\footnote{
%     Reliability can be achieved in unreliable networks by resending messages or using some error correction code.
% }.

@@

% TODO big N does not follow our convention
In our model, we consider $N$ nodes, which is the population size.
$n$ of them are facilitators, $t$ nodes are malicious and the inequality
$n \ge 3t + 1$ must hold.
This inequality is from the work of Pease, Shostak and Lamport, where they show a network of $n$ nodes cannot reach Byzantine agreement for $t \ge n/3$~\cite{pease1980reaching}.
Further, the inequality $N \ge n + t$ must also hold so that there are enough honest nodes in the network to run the consensus protocol;
the exact reason becomes apparent in~\Cref{sec:consensus-phase}.

@@

\section{Extended TrustChain}
The primary data structure used in our system is the Extended TrustChain.
Each node $u$ has a public and private key pair---$pk_u$ and $sk_u$, and a chain $B_u$.
The chain consist of blocks $B_u = \{ b_{u, i} : i \in \{ 0, \dots, h - 1 \} \}$,
where $b_{u, i}$ is the $i$th block of $u$,
and $h$ is the height of the block (i.e. $h = |B_u|$).
We use $b_{u, h-1}$ to denote the latest block.
There are two types of blocks, TX blocks and CP blocks.
If $T_u$ is the set of all TX blocks in $B_u$ and $C_u$ is the set of all CP blocks is $B_u$,
then $T_u \cup C_u = B_u$ and $T_u \cap C_u = \varnothing$.
The notation $b_{u, i}$ is generic over the block type.
% We assume there exists a function $\textsf{typeof}: B_u \rightarrow \{ \tau, \gamma \}$ that returns the type of the block,
% where $\tau$ represents the TX type and $\gamma$ represents the CP type.

@@

The TX block is a six-tuple, i.e.
$$t_{u, i} = \langle \textsf{H}(b_{u, i - 1}), seq_u, txid, pk_v, m, sig_u \rangle.$$
We describe each item in turn.
\begin{enumerate}
\item $\textsf{H}(b_{u, i - 1})$ is the hash pointer to the previous block.
\item $seq_u$ is the sequence number, which should equal $i$.
\item $txid$ is the transaction identifier, it should be generated using a cryptographically secure pseudo-random number generator by the initiator of the transaction.
\item $pk_v$ is the public key of the counterparty $v$.
\item $m$ is the transaction message.
\item $sig_u$ is the signature created using $sk_u$ on the concatenation of the binary representation of the five items above.
\end{enumerate}
The fact that we have no constraint on the content of $m$ is in alignment with our design goal---application neutrality.

TX blocks come in pairs.
In particular, for every TX block 
$$t_{u, i} = \langle \textsf{H}(b_{u, i - 1}), seq_u, txid, pk_v, m, sig_u \rangle$$
there exist one and only one pair 
$$t_{v, j} = \langle \textsf{H}(b_{v, j - 1}), seq_v, txid, pk_u, m, sig_v \rangle,$$
if they are created by honest nodes running the TX protocol.
Note that the $txid$ and $m$ are the same, and the public keys refer to each other.
Thus, given a TX block, these properties allow us to identify its pair.
\end{definition}

@@

Our consensus protocol runs in rounds,
where the first round is defined to be 1 and it is incremented after every execution of the consensus protocol.
The consensus result, output of the consensus protocol, is a tuple, i.e. 
$$\C_r = \langle r, C \rangle,$$
where $C$ is a set of CP blocks agreed by the facilitators of round $r$.
\end{definition}

Now we define an important property which results from the interleaving nature of CP and TX blocks.
It is used in our validation protocol.
\begin{definition}
\textbf{\emph{Enclosure and agreed enclosure}}

@@

If the enclosure of some TX block $t_{u, i}$ is $\langle c_{u,a}, c_{u, b} \rangle$,
then its fragment $F_{u, i}$ is defined as $\{ b_{u, i} : a \le i \le b \}$.
Similarly, agreed fragment has the same definition as fragment but using agreed enclosure.
For convenience, the function $\textsf{agreed\_fragment}(t_{u, i})$ outputs the agreed fragment of $t_{u, i}$ if it exists, otherwise $\bot$.
\end{definition}

@@

Our consensus protocol $\Pi_c$ runs on top of the Extended TrustChain.
It uses an unmodified asynchronous common subset (ACS) algorithm as the key building block.
The objectives of the protocol are to
    allow honest nodes to make progress (in the form of creating new CP blocks),
    compute correct the consensus result in every round
    and have an unbiased election of facilitators.
We formally define the desired properties below.
\begin{definition}
\label{def:consensus}
\textbf{\emph{TrustChain consensus protocol}}

@@

There are $n$ nodes, of which at most $t$ might experience Byzantine fault.
Node $i$ starts with a non-empty set of input values $C_i$.
The nodes must decide an output $C$, satisfying the following.
\begin{enumerate}
    \item \emph{Agreement:}
        If a correct node outputs $C$, then every correct node outputs $C$.
    \item \emph{Validity:}
        If any correct node outputs a set $C$,
        then $|C| \ge n - t$ and $C$ contains the input of at least $n - 2t$ nodes.
    \item \emph{Termination:}
        If $n - t$ nodes receive an input, then all correct nodes produce an output.
\end{enumerate}
\end{definition}

ACS has the nice property of censorship resilience when compared to other consensus algorithms.
In PBFT~\cite{castro1999practical}, a leader is elected, if the leader is malicious but follows the protocol, then it can selectively filter values.
In contrast, every party in ACS are involved in the proposal phase,
and it guarantees that if $n - 2t$ parties propose the same value, then it must be in the agreed output.
In other words, if some value is submitted to at least $n - 2t$ nodes, it is guaranteed to be in the consensus result.
For a detailed description of ACS, we refer to the HoneyBadgerBFT work~\cite{miller2016honey}.
To understand the remainder of this work, the knowledge of~\Cref{def:acs} is sufficient.

@@

To bootstrap, imagine that there is some bootstrap oracle that initiates the correct program on every node,
meaning that it satisfied the properties in \Cref{def:consensus}.
In practice, the bootstrap oracle is most likely the software developer that sets up the system and assigns the facilitators of round 1 in a fair way.
This concludes the bootstrap phase.
For any future rounds, the consensus phase is used.

\subsection{Consensus phase}
\label{sec:consensus-phase}
For any node $u$,
the consensus phase begins when $\F_r$ is available and the latest block is $c_{u, h-1}$.
Note that $\F_r$ indicates the facilitators that were elected using results of round $r$ and are responsible for driving the ACS algorithm in round $r + 1$.
The goal is to reach agreement on a set of new facilitators $\F_{r + 1}$ that satisfies the four properties in \Cref{def:consensus}.

There are two scenarios in the consensus phase.
First, if $u$ is not the facilitator, it sends $\langle \texttt{cp\_msg}, c_{u, h-1} \rangle$ to all the facilitators.
Second, if $u$ is a facilitator, it waits until $N - t$ messages of type \texttt{cp\_msg} are received.
% Second if the node is a facilitator, it waits for some duration $D$ and collect messages of type \texttt{cp\_msg}, where $D \gg \Delta$.
Invalid messages are removed.
That is blocks with invalid signatures and blocks signed by the same key.
With the sufficient number of \texttt{cp\_msg} messages,
it begins the ACS algorithm and some $\C'_{r + 1}$ should be agreed upon by the end of it.
Duplicates and blocks with invalid signatures are again removed from $\C'_{r+1}$ and we call the final result $\C_{r+1}$.
We have to remove invalid blocks a second time because the adversary may send different CP blocks to different facilitators,
which results in invalid blocks in the ACS output, but not in any of the inputs.

@@

Continuing, when $\F_{r}$ finish the ACS execution and reach agreement on $\C_{r+1}$,
they immediately broadcast two messages to all the nodes---first the consensus message $\langle \texttt{cons\_msg}, \C_{r+1} \rangle$,
and second the signature message $\langle \texttt{cons\_sig}, r, sig \rangle$.
The reason for sending \texttt{cons\_sig} is the following.
The channels are not authenticated, 
and there are no signatures in $\C_{r + 1}$.
If a non-facilitator sees some $\C_{r + 1}$, it cannot immediately trust it because it may have been forged.
Thus, to guarantee authenticity, every facilitator sends an additional message that is the signature of $\C_{r + 1}$.

@@

The TX protocol $\Pi_t$, shown in \Cref{alg:tx-proto}, is run by all nodes.
It is also known as True Halves, first described informally by Veldhuisen~\cite[Chapter~3.2]{truehalves}.
Nodes that wish to initiate a transaction calls $\textsf{new\_tx}(pk_v, m, txid)$ (\Cref{alg:new-tx}) with the intended counterparty $v$ identified by $pk_v$ and message $m$.
$txid$ should be a uniformly distributed random value, i.e. $txid \in_R \{0, 1\}^{256}$.
Then the initiator sends $\langle \texttt{tx\_req}, t_{u, h}\rangle$ to $v$.

@@

The consensus protocol and the transaction protocol do not provide a mechanism to detect tampering.
The validation protocol aims to solve this issue.
The protocol is also a request-response protocol.
It assumes that nodes store all the consensus results as well as the corresponding signatures that they are aware of.
Further, we assume nodes that recovered from a crash or a corruption are able to recover its missed \texttt{cons\_msg} and \texttt{cons\_sig} messages,
which can be achieved by querying other nodes.
But before explaining the protocol itself, we first define what it means for a transaction to be valid.

@@

\begin{algorithm}
\caption{Function $\textsf{get\_validity}(t_{u, i}, F_{u, i}, F_{v, j})$ validates the transaction represented by $t_{u, i}$.
We assume $F_{u, i}$ is correct and contains $t_{u, i}$.
$F_{v, j}$ is the corresponding fragment received from $v$.}
\label{alg:get-validity}

@@

A TrustChain validation protocol is correct if the following properties hold.
\begin{enumerate}
    \item \emph{Agreement}:
        If any correct node decides on the validity of a transaction, except when it is \emph{unknown},
        then all other correct nodes are able to reach the same conclusion or output \emph{unknown}.
    \item \emph{Validity}:
        The validation protocol outputs the correct result
        according to the validity definition above.
    % \item \emph{Unforgeability}:
    %     If some transaction is valid, it cannot be forged into an invalid transaction.
    %     If some transaction is invalid, it cannot be forged into a valid transaction.
    \item \emph{Liveness}:
        Any valid (invalid) transaction is marked as valid (invalid) eventually.
\end{enumerate}
\end{definition}

### 2017-08-23 thesis/chapters/ch4-analysis.tex
Rearrange figures; edit

\begin{lemma}
\label{lemma:validity}
If for an arbitrary round $r$,
$\F_r$ is known by all correct nodes and any correct node outputs $\F_{r+1}$,
then (a) $|\C_{r+1}| \ge N - t$ and (b) $|\F_{r+1}| = n$.
\end{lemma}
\begin{proof}
The validity follows from the validity property of ACS and the definition of our model,
namely $N \ge n + t$ and $n \ge 3t + 1$.
Given $\F_r$, since $N \ge n + t$ , there is at least $n$ nodes that would send their CP block to $\F_r$.
From the validity property of ACS, we know the output must contain the input of at least $n - 2t$ nodes.
But $n -t$ facilitators must have received $N - t$ valid CP blocks, so $|\C_{r+1}| \ge N-t$ and this proves (a).
Since $N-t \ge (n+t) -t = n$ and $\textsf{get\_facilitators}(\C_{r+1})$ outputs $n$ items, so $|\F_{r+1}| = n$ and this proves (b).
\end{proof}

\begin{lemma}
\label{lemma:fairness}
If for an arbitrary round $r$,
$\F_r$ is known by all correct nodes then
every node with a CP block in $\C_{r+1}$ should have an equal probability to be elected as a facilitator in $\F_{r+1}$.
\end{lemma}
\begin{proof}
We already established that $|\C_{r+1}| \ge N - t \ge n$ from \Cref{lemma:validity}.
Then the proof directly follows from the random oracle model.
Recall that the luck value is computed using $\textsf{H}(\C_{r+1} || pk_u)$.
Since $pk_u$ is unique for every node that has a CP block in $\C_{r+1}$,
the output of $\textsf{H}(\cdot)$ is uniformly random.
As a result, the output of $\textsf{get\_facilitators}(\C_{r+1})$ is a random permutation of all the nodes in $\C_{r+1}$ truncated to $n$.
Thus, every node has the same probability of becoming a facilitator.
\end{proof}

>>>>

\begin{lemma}
\label{lemma:validity}
If for an arbitrary round $r$,
$\F_r$ is known by all correct nodes and any correct node outputs $\F_{r+1}$,
then (a) $|\C_{r+1}| \ge N - t$ and (b) $|\F_{r+1}| = n$.
\end{lemma}
\begin{proof}
The validity follows from the validity property of ACS and the definition of our model,
namely $N \ge n + t$ and $n \ge 3t + 1$.
Given $\F_r$, since $N \ge n + t$ , there is at least $n$ nodes that would send their CP block to $\F_r$.
From the validity property of ACS, we know the output must contain the input of at least $n - 2t$ nodes.
But $n -t$ facilitators must have received $N - t$ valid CP blocks, so $|\C_{r+1}| \ge N-t$ and this proves (a).
Since $N-t \ge (n+t) -t = n$ and $\textsf{get\_facilitators}(\C_{r+1}, n)$ outputs $n$ items, so $|\F_{r+1}| = n$ and this proves (b).
\end{proof}

\begin{lemma}
\label{lemma:fairness}
If for an arbitrary round $r$,
$\F_r$ is known by all correct nodes then
every node with a CP block in $\C_{r+1}$ should have an equal probability to be elected as a facilitator in $\F_{r+1}$.
\end{lemma}
\begin{proof}
We already established that $|\C_{r+1}| \ge N - t \ge n$ from \Cref{lemma:validity}.
Then the proof directly follows from the random oracle model.
Recall that the luck value is computed using $\textsf{H}(\C_{r+1} || pk_u)$.
Since $pk_u$ is unique for every node that has a CP block in $\C_{r+1}$,
the output of $\textsf{H}(\cdot)$ is uniformly random.
As a result, the output of $\textsf{get\_facilitators}(\C_{r+1}, n)$ is a random permutation of all the nodes in $\C_{r+1}$ truncated to $n$.
Thus, every node has the same probability of becoming a facilitator.
\end{proof}
